---
title: "Adrenocortical and autonomic cross-system regulation in youth: A meta-analysis"
author: "Meriah DeJoseph"
date: "2021-2023"
output: html_document
---

Adrenocortical and autonomic cross-system regulation in youth: A meta-analysis. PROPSERO preregistration (ID #244929) can be found here: https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=244929

All analyses for this meta-analysis are below using the metafor package, thanks to the guidance from this OSF tutorial:
https://osf.io/q8stz/?view_only=
Moreau, D., & Gamble, B. (2022). Conducting a Meta-Analysis in the Age of Open Science: Tools, Tips, and Practical Recommendations. Psychological Methods, 27 (3), 426-432.

For this project, we are using multivariate mixed-effects meta regression models based on rationale from Cheung 2019 (which compared multivariate vs. 3-level multilevel models for meta-analyses).

### Load libraries and data
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
# Load libraries
library(pacman)
library(tidyverse)
library(metafor)

# Set wd
setwd("/Users/meriahdejoseph/Library/CloudStorage/Box-Box/!ICD/Meta-Analysis/Analyses/R2 re-run analyses")

# Import data & remove rows without effect sizes
rawdf <- read_csv("Coding sheet_8.15.23.csv")
rawdf$ES <- as.numeric(rawdf$ES)
df <- rawdf %>% 
  drop_na(ES)

#Quick descriptives needed for paper:
descript <- df %>% 
  filter(ES_ID == 1) %>% 
  summarise(Mean = mean(AGE_MEAN_YRS, na.rm=TRUE),
            SD = sd(AGE_MEAN_YRS, na.rm=TRUE),
            R = range(AGE_MEAN_YRS, na.rm=TRUE))


```

### Calculate basic effect sizes and variance
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
# Calculate effect size and variances using escalc() function from metafor package

# from correlations (Pearson's r)
es_from_r <- escalc(measure = "COR",         # we are generating r values
                    ri = ES,                  # the inputted r values
                    ni = N,                  # column containing total sample size
                    data = df,               # dataframe
                    slab = REF)              # study labels

# effect sizes calculated above
es <- es_from_r$yi

# variances calculated above
variance <- es_from_r$vi

#lower <- exp(es_from_r$yi - 1.96*sqrt(es_from_r$vi))
#upper <- exp(es_from_r$yi + 1.96*sqrt(es_from_r$vi))

# append the new effect sizes and variances to the main data frame
df <- cbind(df, es, variance)

# Note that the two examples of effect sizes provided above are not exhaustive--other types of effect sizes can be encountered in meta-analyses (e.g., odds ratio, risk ratio), for which the present script can easily be adapted.

#save out refs for forest list
refs <- as.data.frame(df$REF)
ES2 <- as.data.frame(df$es)
relat <- as.data.frame(df$RELATION)
refs <- cbind(refs, relat, ES2)
write.csv(refs,"refs.csv")

```

### Multivariate mixed effects meta regression model 
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

main_model <- rma.mv(ES, variance, mods = ~ RELATION - 1,
              random = ~ RELATION | ID, 
              struct = "UN",
              slab = REF,
              method = "ML",
              data =df)
print(main_model, digits = 3)

# This is what Berkey et al. (1998) call a multivariate maximum likelihood (MML) random-effects model. Note that rma.mv() uses REML estimation by default, so
# method="ML"must be explicitly requested. The random = ~ outcome | study ID
# part adds random effects for each outcome within each study to the model. With
# struct="UN", the random effects are allowed to have different variances for each outcome and are allowed to be correlated.
#https://www.metafor-project.org/doku.php/analyses:berkey1998
# Berkey, C. S., Hoaglin, D. C., Antczak-Bouckoms, A., Mosteller, F., & Colditz, G. A. (1998). Meta-analysis of multiple outcomes by regression with random effects. Statistics in Medicine, 17(22), 2537–2550.
```

### Get range of rs to report in results
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

df %>% 
  filter(RELATION=="HPA-SNS baseline") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

df %>% 
  filter(RELATION=="HPA-SNS reactivity") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

df %>% 
  filter(RELATION=="HPA-PNS baseline") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

df %>% 
  filter(RELATION=="HPA-PNS reactivity") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

df %>% 
  filter(RELATION=="SNS-PNS baseline") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

df %>% 
  filter(RELATION=="SNS-PNS reactivity") %>% 
  summarize(mean = mean(ES, na.rm = TRUE),
            min = min(ES, na.rm = TRUE),
            max = max(ES, na.rm = TRUE))

```

### Calculate heterogeneity
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

# Calculate the I^2 statistic for a multilevel model
# Tells you proportion of variation across the inc effect sizes that's likely to due real diff
# between those studies rather than diff due to random variation and error 
# Using the formula from www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate

V <- bldiag(df$variance)
W <- solve(V)
X <- model.matrix(main_model)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
I2_statistic <- 100 * main_model$tau2 / (main_model$tau2 + (main_model$k-main_model$p)/sum(diag(P)))

#Percentage of variation across effects sizes are actually due to real diff between studies
#            estim   sqrt  k.lvl  fixed               level 
# tau^2.1    0.002  0.047     16     no    HPA-PNS baseline 
# tau^2.2    0.022  0.147     20     no  HPA-PNS reactivity 
# tau^2.3    0.005  0.072     30     no    HPA-SNS baseline 
# tau^2.4    0.018  0.135     43     no  HPA-SNS reactivity 
# tau^2.5    0.002  0.042     11     no    SNS-PNS baseline 
# tau^2.6    0.036  0.189     13     no  SNS-PNS reactivity 
#25.44019 77.03865 44.78483 73.79755 21.40558 84.71884
#23.06003 65.19464 43.39072 73.62356 26.25312 83.08556

```

### Create combined forest plot
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

# Save output as pdf
pdf("ForestPlot.pdf", family = "Helvetica", width = 12, height = 25)

# Decrease margins so the full space is used
par(mar=c(2.5,4,1,2.5), cex = .9, font = 1)

# Create the forest plot
forest(main_model, 
       xlim = c(-2.5, 1.8),                 # adjust horizontal plot region limits
       #order ="obs",                        # order by effect size
       addfit = F,                          # add standard summary polygon
       annotate = T,                        # remove annotations
       width = 0,                           # width of annotations
       efac = .55,                          # height of CI bars
       pch = 19,                            # changing point symbol to filled circle
       col = "gray40",                      # change color of points/CIs
       clim = c(-1 ,1),                     # set absolute limits for CIs
       cex.lab = 1,                         # increase size of x-axis title
       cex.axis = 1,                        # increase size of x-axis labels
       cex = .85,                           # set font expansion factor
       lty = c("solid",                     # CI line type
               "solid",                     # credibility interval line type
               "solid"),                    # horizontal line type
       xlab = "",                           # label X axis
       mlab = "RE Model: p = .04, I2 = 93.9",    # label summary estimate
       showweights=F,  
       ilab=df$RELATION, 
       ilab.xpos=-1.1, 
       steps = 5)                           # number of tick marks for the x-axis

# Switch to bold font
par(cex = .9, font = 2)

# Add column headings to the plot
text(-2.5, 135, "Study name", pos = 4, cex = .9)
text(1.8, 135, "Correlation and 95% CI", pos = 2, cex = .9)
text(-1.1, 135, "Outcome", font=2)

# Close off set par back to the original settings
dev.off()

op <- par(cex = .9, font = 1)
par(op)

#Use this plot to extract the individual effects in the format needed for the better publication plots below

```

### HPA-SNS plots using forestplot function
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
#Note: this code is messy but was the quickest way to get this in format needed for the forestplot function
#used this: https://github.com/brandonyph/Forest-Plot-R-Introduction

library(forestplot)
fordata <- read.csv("Forest data.csv") 

#######################
#HPASNSbase
#######################
forHPASNSbase <- fordata %>% filter(Relation == "HPA-SNS baseline")
forHPASNSbase <- as.tibble(forHPASNSbase)

 forHPASNSbase <- forHPASNSbase %>% 
  mutate(Index2 = row_number())
 
forHPASNSbase <- forHPASNSbase %>% 
  mutate(mean = R, 
         summary = "")

forHPASNSbase$R <- as.character(forHPASNSbase$R)
forHPASNSbase$summary <- as.logical(forHPASNSbase$summary)

#add top part
forHPASNSbase <- forHPASNSbase %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forHPASNSbase <- forHPASNSbase %>% 
  add_row(Index2 = 0)

#sort by index
forHPASNSbase <- forHPASNSbase[order(forHPASNSbase$Index2),]

#add bottom part
forHPASNSbase<- forHPASNSbase %>% 
  add_row()
forHPASNSbase <- forHPASNSbase %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.07",
          mean = 0.07,
          LL = 0.03,
          UL = .10)
forHPASNSbase <- forHPASNSbase %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forHPASNSbase <-forHPASNSbase %>% 
  select(study, R, summary, mean, lower, upper)

HPASNSbaseNEW <- forHPASNSbase %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
             #clip = c(-0.5, .5), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "33" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "orangered4",
                            line = "orangered3",
                            summary = "orangered3"))
HPASNSbaseNEW 






#######################
#HPASNSreact
#######################
forHPASNSreact <- fordata %>% filter(Relation == "HPA-SNS reactivity")
forHPASNSreact <- as.tibble(forHPASNSreact)

 forHPASNSreact <- forHPASNSreact %>% 
  mutate(Index2 = row_number())
 
forHPASNSreact <- forHPASNSreact %>% 
  mutate(mean = R, 
         summary = "")

forHPASNSreact$R <- as.character(forHPASNSreact$R)
forHPASNSreact$summary <- as.logical(forHPASNSreact$summary)

#add top part
forHPASNSreact <- forHPASNSreact %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forHPASNSreact <- forHPASNSreact %>% 
  add_row(Index2 = 0)

#sort by index
forHPASNSreact <- forHPASNSreact[order(forHPASNSreact$Index2),]

#add bottom part
forHPASNSreact<- forHPASNSreact %>% 
  add_row()
forHPASNSreact <- forHPASNSreact %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.09",
          mean = 0.09,
          LL = 0.04,
          UL = .14)
forHPASNSreact <- forHPASNSreact %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forHPASNSreact <-forHPASNSreact %>% 
  select(study, R, summary, mean, lower, upper)

HPASNSreactNEW <- forHPASNSreact %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
            #clip = c(-0.5, .5), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "46" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "orangered4",
                            line = "orangered3",
                            summary = "orangered3"))
HPASNSreactNEW 

```

### HPA-PNS plots using forestplot function
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
#Note: this code is messy but was the quickest way to get this in format needed for the forestplot function
library(forestplot)
fordata <- read.csv("Forest data.csv") 

#######################
#HPAPNSbase
#######################
forHPAPNSbase <- fordata %>% filter(Relation == "HPA-PNS baseline")
forHPAPNSbase <- as.tibble(forHPAPNSbase)

 forHPAPNSbase <- forHPAPNSbase %>% 
  mutate(Index2 = row_number())
 
forHPAPNSbase <- forHPAPNSbase %>% 
  mutate(mean = R, 
         summary = "")

forHPAPNSbase$R <- as.character(forHPAPNSbase$R)
forHPAPNSbase$summary <- as.logical(forHPAPNSbase$summary)

#add top part
forHPAPNSbase <- forHPAPNSbase %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forHPAPNSbase <- forHPAPNSbase %>% 
  add_row(Index2 = 0)

#sort by index
forHPAPNSbase <- forHPAPNSbase[order(forHPAPNSbase$Index2),]

#add bottom part
forHPAPNSbase<- forHPAPNSbase %>% 
  add_row()
forHPAPNSbase <- forHPAPNSbase %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.004",
          mean = 0.004,
          LL = -0.043,
          UL = 0.050)
forHPAPNSbase <- forHPAPNSbase %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forHPAPNSbase <-forHPAPNSbase %>% 
  select(study, R, summary, mean, lower, upper)

HPAPNSbaseNEW <- forHPAPNSbase %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
             #clip = c(-0.3, .3), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "19" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "sienna3",
                            line = "sienna2",
                            summary = "sienna2"))
HPAPNSbaseNEW 






#######################
#HPAPNSreact
#######################
forHPAPNSreact <- fordata %>% filter(Relation == "HPA-PNS reactivity")
forHPAPNSreact <- as.tibble(forHPAPNSreact)

 forHPAPNSreact <- forHPAPNSreact %>% 
  mutate(Index2 = row_number())
 
forHPAPNSreact <- forHPAPNSreact %>% 
  mutate(mean = R, 
         summary = "")

forHPAPNSreact$R <- as.character(forHPAPNSreact$R)
forHPAPNSreact$summary <- as.logical(forHPAPNSreact$summary)

#add top part
forHPAPNSreact <- forHPAPNSreact %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forHPAPNSreact <- forHPAPNSreact %>% 
  add_row(Index2 = 0)

#sort by index
forHPAPNSreact <- forHPAPNSreact[order(forHPAPNSreact$Index2),]

#add bottom part
forHPAPNSreact<- forHPAPNSreact %>% 
  add_row()
forHPAPNSreact <- forHPAPNSreact %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.096",
          mean = 0.096,
          LL = 0.036,
          UL = 0.156)
forHPAPNSreact <- forHPAPNSreact %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forHPAPNSreact <-forHPAPNSreact %>% 
  select(study, R, summary, mean, lower, upper)

HPAPNSreactNEW <- forHPAPNSreact %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
            # clip = c(-0.5, .5), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "23" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "sienna3",
                            line = "sienna2",
                            summary = "sienna2"))
HPAPNSreactNEW 

```

### SNS-PNS plots using forestplot function
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
#Note: this code is messy but was the quickest way to get this in format needed for the forestplot function
library(forestplot)
fordata <- read.csv("Forest data.csv") 

#######################
#SNSPNSbase
#######################
forSNSPNSbase <- fordata %>% filter(Relation == "SNS-PNS baseline")
forSNSPNSbase <- as.tibble(forSNSPNSbase)

 forSNSPNSbase <- forSNSPNSbase %>% 
  mutate(Index2 = row_number())
 
forSNSPNSbase <- forSNSPNSbase %>% 
  mutate(mean = R, 
         summary = "")

forSNSPNSbase$R <- as.character(forSNSPNSbase$R)
forSNSPNSbase$summary <- as.logical(forSNSPNSbase$summary)

#add top part
forSNSPNSbase <- forSNSPNSbase %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forSNSPNSbase <- forSNSPNSbase %>% 
  add_row(Index2 = 0)

#sort by index
forSNSPNSbase <- forSNSPNSbase[order(forSNSPNSbase$Index2),]

#add bottom part
forSNSPNSbase<- forSNSPNSbase %>% 
  add_row()
forSNSPNSbase <- forSNSPNSbase %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.02",
          mean = 0.02,
          LL = -0.030,
          UL = 0.075)
forSNSPNSbase <- forSNSPNSbase %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forSNSPNSbase <-forSNSPNSbase %>% 
  select(study, R, summary, mean, lower, upper)

SNSPNSbaseNEW <- forSNSPNSbase %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
            # clip = c(-0.3, .3), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "14" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "palevioletred4",
                            line = "palevioletred3",
                            summary = "palevioletred3"))
SNSPNSbaseNEW 






#######################
#SNSPNSreact
#######################
forSNSPNSreact <- fordata %>% filter(Relation == "SNS-PNS reactivity")
forSNSPNSreact <- as.tibble(forSNSPNSreact)

 forSNSPNSreact <- forSNSPNSreact %>% 
  mutate(Index2 = row_number())
 
forSNSPNSreact <- forSNSPNSreact %>% 
  mutate(mean = R, 
         summary = "")

forSNSPNSreact$R <- as.character(forSNSPNSreact$R)
forSNSPNSreact$summary <- as.logical(forSNSPNSreact$summary)

#add top part
forSNSPNSreact <- forSNSPNSreact %>% 
  add_row(label = "Study", R = "r", Index2 = 0, summary = TRUE)
forSNSPNSreact <- forSNSPNSreact %>% 
  add_row(Index2 = 0)

#sort by index
forSNSPNSreact <- forSNSPNSreact[order(forSNSPNSreact$Index2),]

#add bottom part
forSNSPNSreact<- forSNSPNSreact %>% 
  add_row()
forSNSPNSreact <- forSNSPNSreact %>% 
  add_row(label = "Summary",  summary = TRUE,
          R  = "0.004",
          mean = 0.004,
          LL = -0.095,
          UL = 0.103)
forSNSPNSreact <- forSNSPNSreact %>% 
  rename(lower = LL,
         upper = UL,
         study = label)

forSNSPNSreact <-forSNSPNSreact %>% 
  select(study, R, summary, mean, lower, upper)

SNSPNSreactNEW <- forSNSPNSreact %>% 
  forestplot(labeltext = c(study, R), 
             is.summary = summary,
             #clip = c(-0.5, .5), 
             hrzl_lines = list("3" = gpar(lty = 2), 
                               "16" = gpar(lwd = 1, columns = 1:3, 
                                        col = "#000044")),
             col = fpColors(box = "palevioletred4",
                            line = "palevioletred3",
                            summary = "palevioletred3"))
SNSPNSreactNEW 

```

### Moderator analyses -- methods covars
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

#Note: model output for categ moderators gives estimated effect sizes for that group, not in relation to intercept

### Methods moderators ###

# Time of day
#First need to better categorize because low cell counts for some
df$TIMEOFDAY <- as.factor(df$TIMEOFDAY)
df <- df %>% 
  mutate(TIMEOFDAY2 = case_when(TIMEOFDAY == 'Afternoon' ~ 'Afternoon_Evening', 
                        TIMEOFDAY == 'Afternoon and Evening' ~ 'Afternoon_Evening', 
                        TIMEOFDAY == 'Evening' ~ 'Afternoon_Evening',
                        TIMEOFDAY == 'Morning' ~ 'Morning_Afternoon',
                        TIMEOFDAY == 'Morning and Afternoon' ~ 'Morning_Afternoon',
                        TIMEOFDAY == 'Does not specify' ~ as.character(NA)))
table(df$TIMEOFDAY)
table(df$TIMEOFDAY2) 
df$TIMEOFDAY2 <- as.factor(df$TIMEOFDAY2)

moderator_time <- rma.mv(ES, variance, 
                     mods = ~ RELATION:I(TIMEOFDAY2) - 1,
              random = ~ RELATION | ID, 
              struct = "UN",
              slab = REF,
              method = "ML",
              data =df)
print(moderator_time, digits = 3)

#Get ks
k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "HPA-SNS baseline"), ]
#5
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "HPA-SNS baseline"), ]
#23
k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "HPA-SNS reactivity"), ]
#5
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "HPA-SNS reactivity"), ]
#34

k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "HPA-PNS baseline"), ]
#3
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "HPA-PNS baseline"), ]
#11
k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "HPA-PNS reactivity"), ]
#4
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "HPA-PNS reactivity"), ]
#13

k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "SNS-PNS baseline"), ]
#2
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "SNS-PNS baseline"), ]
#7
k <- df[which(df$TIMEOFDAY2 == "Morning_Afternoon" & df$RELATION ==  "SNS-PNS reactivity"), ]
#2
k <- df[which(df$TIMEOFDAY2 == "Afternoon_Evening" & df$RELATION ==  "SNS-PNS reactivity"), ]
#8





# Task type
#First need to recode
df$STRESS_TASK <- as.factor(df$STRESS_TASK)
df <- df %>% 
  mutate(STRESS_TASK2 = case_when(STRESS_TASK == 'Challenge or Emotional Reactivity Task' ~ 'Other', 
                        STRESS_TASK == 'Lab Tab' ~ 'Other', 
                        STRESS_TASK == 'Other' ~ 'Other',
                        STRESS_TASK == 'TSST' ~ 'TSST',
                        STRESS_TASK == 'TSST speech only' ~ 'TSST',
                        STRESS_TASK == 'TSST math only' ~ 'TSST'))
table(df$STRESS_TASK)
df$STRESS_TASK2 <- as.factor(df$STRESS_TASK2)
table(df$STRESS_TASK2)

moderator_task <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(STRESS_TASK2) - 1,
              random = ~ RELATION | ID,
              #struct = "UN", #did not converge
              slab = REF,
              data =df)
print(moderator_task, digits = 3)


#Get ks
k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="HPA-SNS baseline"), ]
#25
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="HPA-SNS baseline"), ]
#5
k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="HPA-SNS reactivity"), ]
#37
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="HPA-SNS reactivity"), ]
#6

k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="HPA-PNS baseline"), ]
#13
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="HPA-PNS baseline"), ]
#3
k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="HPA-PNS reactivity"), ]
#15
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="HPA-PNS reactivity"), ]
#5

k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="SNS-PNS baseline"), ]
#11
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="SNS-PNS baseline"), ]
#0
k <- df[which(df$STRESS_TASK2 == "TSST" & df$RELATION =="SNS-PNS reactivity"), ]
#12
k <- df[which(df$STRESS_TASK2 == "Other" & df$RELATION =="SNS-PNS reactivity"), ]
#1





####Reactivity method####

#HPA react method

#First filter by reactivity relations
df$HPA_REACT<- as.factor(df$HPA_REACT)

dfHPA <- df %>% 
  filter(RELATION != "SNS-PNS reactivity") %>% 
  filter(RELATION != "SNS-PNS baseline") %>% 
  filter(RELATION != "HPA-SNS baseline") %>% 
  filter(RELATION != "HPA-PNS baseline") 

table(dfHPA$HPA_REACT) 
#low cell counts, so going to merge some 

dfHPA <- dfHPA%>% 
  mutate(HPA_REACT2 = case_when(HPA_REACT == 'Mean score' ~ 'Other', 
                        HPA_REACT == 'Peak score' ~ 'Other', 
                        HPA_REACT == 'Residualized change' ~ 'Difference score', 
                        HPA_REACT == 'AUC' ~ 'AUC',
                        HPA_REACT == 'Other' ~ 'Other',
                        HPA_REACT == 'Percent change' ~ 'Difference score',
                        HPA_REACT == 'Difference score' ~ 'Difference score'))
table(dfHPA$HPA_REACT2) 

moderator_HPAreact <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(HPA_REACT2) - 1,
              random = ~ RELATION | ID,
              struct = "UN", 
              slab = REF,
              data =dfHPA)
print(moderator_HPAreact, digits = 3)


#Get ks

k <- dfHPA[which(dfHPA$HPA_REACT2 == "AUC" & dfHPA$RELATION =="HPA-SNS reactivity"), ]
#11
k <- dfHPA[which(dfHPA$HPA_REACT2 == "Difference score" & dfHPA$RELATION =="HPA-SNS reactivity"), ]
#22
k <- dfHPA[which(dfHPA$HPA_REACT2 == "Other" & dfHPA$RELATION =="HPA-SNS reactivity"), ]
#9



k <- dfHPA[which(dfHPA$HPA_REACT2 == "AUC" & dfHPA$RELATION =="HPA-PNS reactivity"), ]
#2
k <- dfHPA[which(dfHPA$HPA_REACT2 == "Difference score" & dfHPA$RELATION =="HPA-PNS reactivity"), ]
#9
k <- dfHPA[which(dfHPA$HPA_REACT2 == "Other" & dfHPA$RELATION =="HPA-PNS reactivity"), ]
#9






#SNS react method

df$SNS_REACT<- as.factor(df$SNS_REACT)

dfSNS <- df %>% 
  filter(RELATION != "HPA-PNS reactivity") %>% 
  filter(RELATION != "SNS-PNS baseline") %>% 
  filter(RELATION != "HPA-SNS baseline") %>% 
  filter(RELATION != "HPA-PNS baseline") 

table(dfSNS$SNS_REACT) 
#low cell counts, so going to merge some with "other"

dfSNS <- dfSNS%>% 
  mutate(SNS_REACT2 = case_when(SNS_REACT == 'Mean score' ~ 'Other', 
                        SNS_REACT == 'Peak score' ~ 'Other', 
                        SNS_REACT == 'Residualized change' ~ 'Difference score', 
                        SNS_REACT == 'AUC' ~ 'AUC',
                        SNS_REACT == 'Other' ~ 'Other',
                        SNS_REACT == 'Percent change' ~ 'Difference score',
                        SNS_REACT == 'Difference score' ~ 'Difference score'))
table(dfSNS$SNS_REACT2) 

moderator_SNSreact <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(SNS_REACT2) - 1,
              random = ~ RELATION | ID,
              struct = "UN", 
              slab = REF,
              data =dfSNS)
print(moderator_SNSreact, digits = 3)


#Get ks

k <- dfSNS[which(dfSNS$SNS_REACT2 == "AUC" & dfSNS$RELATION =="HPA-SNS reactivity"), ]
#10
k <- dfSNS[which(dfSNS$SNS_REACT2 == "Difference score" & dfSNS$RELATION =="HPA-SNS reactivity"), ]
#25
k <- dfSNS[which(dfSNS$SNS_REACT2 == "Other" & dfSNS$RELATION =="HPA-SNS reactivity"), ]
#7


k <- dfSNS[which(dfSNS$SNS_REACT2 == "AUC" & dfSNS$RELATION =="SNS-PNS reactivity"), ]
#2
k <- dfSNS[which(dfSNS$SNS_REACT2 == "Difference score" & dfSNS$RELATION =="SNS-PNS reactivity"), ]
#6
k <- dfSNS[which(dfSNS$SNS_REACT2 == "Other" & dfSNS$RELATION =="SNS-PNS reactivity"), ]
#5



#PNS react method

df$PNS_REACT<- as.factor(df$PNS_REACT)

dfPNS <- df %>% 
  filter(RELATION != "HPA-SNS reactivity") %>% 
  filter(RELATION != "SNS-PNS baseline") %>% 
  filter(RELATION != "HPA-SNS baseline") %>% 
  filter(RELATION != "HPA-PNS baseline") 
  
table(dfPNS$PNS_REACT) 
#low cell counts, so going to merge some 

dfPNS <- dfPNS%>% 
  mutate(PNS_REACT2 = case_when(PNS_REACT == 'Mean score' ~ 'Mean score', 
                        PNS_REACT == 'Residualized change' ~ 'Difference score', 
                        PNS_REACT == 'Other' ~ 'Other',
                        PNS_REACT == 'Adjusted difference score' ~ 'Difference score',
                        PNS_REACT == 'Difference score' ~ 'Difference score'))
table(dfPNS$PNS_REACT2) 

moderator_PNSreact <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(PNS_REACT2) - 1,
              random = ~ RELATION | ID,
              struct = "UN", 
              slab = REF,
              data =dfPNS)
print(moderator_PNSreact, digits = 3)


#Get ks

k <- dfPNS[which(dfPNS$PNS_REACT2 == "Difference score" & dfPNS$RELATION =="HPA-PNS reactivity"), ]
#11
k <- dfPNS[which(dfPNS$PNS_REACT2 == "Other" & dfPNS$RELATION =="HPA-PNS reactivity"), ]
#2 NOW 0 after recode
k <- dfPNS[which(dfPNS$PNS_REACT2 == "Mean score" & dfPNS$RELATION =="HPA-PNS reactivity"), ]
#7 NOW 9 after recode

k <- dfPNS[which(dfPNS$PNS_REACT2 == "Difference score" & dfPNS$RELATION =="SNS-PNS reactivity"), ]
#7 NOW 8 after recode
k <- dfPNS[which(dfPNS$PNS_REACT2 == "Other" & dfPNS$RELATION =="SNS-PNS reactivity"), ]
#2 NOW 0 after recode
k <- dfPNS[which(dfPNS$PNS_REACT2 == "Mean score" & dfPNS$RELATION =="SNS-PNS reactivity"), ]
#4 NOW 5 after recode

```

### Moderator analyses -- participant characteristics
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}
### Sample characteristic moderators ###


# Age
df <- df %>%
  mutate(AGE_MEAN_YRSC = AGE_MEAN_YRS - mean(AGE_MEAN_YRS))
           
moderator_age <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(AGE_MEAN_YRSC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              #struct = "UN", #did not converge
              data =df)
print(moderator_age, digits = 3)


#Recode age to be child (m age =< 11.99 vs. adolescent m age => 12)
df <- df %>%
  mutate(AGE_MEAN_YRS2 = case_when(AGE_MEAN_YRS <= 11.99 ~ 'Child',
                        AGE_MEAN_YRS >= 12 ~ 'Adolescent'))
table(df$AGE_MEAN_YRS2)

#Dichotomized age
moderator_agedi <- rma.mv(ES, variance,
              mods = ~ RELATION:I(AGE_MEAN_YRS2) - 1,
              random = ~ RELATION | ID,
              slab = REF,
              method = "ML",
              #struct = "UN",#did not converge
              data =df)
print(moderator_agedi, digits = 3)

#Get ks
k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="HPA-SNS baseline"), ]
#13
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="HPA-SNS baseline"), ]
#17
k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="HPA-SNS reactivity"), ]
#19
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="HPA-SNS reactivity"), ]
#24

k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="HPA-PNS baseline"), ]
#6
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="HPA-PNS baseline"), ]
#10
k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="HPA-PNS reactivity"), ]
#9
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="HPA-PNS reactivity"), ]
#11

k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="SNS-PNS baseline"), ]
#4
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="SNS-PNS baseline"), ]
#7
k <- df[which(df$AGE_MEAN_YRS2 == "Child" & df$RELATION =="SNS-PNS reactivity"), ]
#5
k <- df[which(df$AGE_MEAN_YRS2 == "Adolescent" & df$RELATION =="SNS-PNS reactivity"), ]
#8





# Puberty -- 9 ppl
df <- df %>%
  mutate(PUBERTYC = PUBERTY - mean(PUBERTY, na.rm=T))
moderator_puberty <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(PUBERTYC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              struct = "UN", 
              data =df)
print(moderator_puberty, digits = 3)



# Percent female 
df <- df %>%
  mutate(SEX_PFEMALEC = SEX_PFEMALE - mean(SEX_PFEMALE, na.rm=T))

moderator_sex <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(SEX_PFEMALEC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              struct = "UN",
              data =df)
print(moderator_sex, digits =3)


# Percent White
df <- df %>%
  mutate(RACE_PWHITEC = RACE_PWHITE - mean(RACE_PWHITE, na.rm=T))

moderator_white <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(RACE_PWHITEC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              #struct = "UN", #did not converge
              data =df)
print(moderator_white, digits = 3)


#Percent Black
df <- df %>%
  mutate(RACE_PBLACKC = RACE_PBLACK - mean(RACE_PBLACK, na.rm=T))

moderator_black <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(RACE_PBLACKC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              struct = "UN",
              data =df)
print(moderator_black, digits = 3)

#Percent Hispanic 
df <- df %>%
  mutate(RACE_PHISPANICC = RACE_PHISPANIC - mean(RACE_PHISPANIC, na.rm=T))

moderator_hispanic <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(RACE_PHISPANICC),
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              struct = "UN",
              data =df)
print(moderator_hispanic, digits = 3)




# SES
df$Low_SES <- as.factor(df$Low_SES)
moderator_SES <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(Low_SES) - 1,
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
             # struct = "UN",
              data =df)
print(moderator_SES, digits = 3)
table(df$Low_SES)


#Get ks
k <- df[which(df$Low_SES == 0 & df$RELATION =="HPA-SNS baseline"), ]
#12
k <- df[which(df$Low_SES == 1 & df$RELATION =="HPA-SNS baseline"), ]
#10
k <- df[which(df$Low_SES == 0 & df$RELATION =="HPA-SNS reactivity"), ]
#17
k <- df[which(df$Low_SES == 1 & df$RELATION =="HPA-SNS reactivity"), ]
#12

k <- df[which(df$Low_SES == 0 & df$RELATION =="HPA-PNS baseline"), ]
#10
k <- df[which(df$Low_SES == 1 & df$RELATION =="HPA-PNS baseline"), ]
#3
k <- df[which(df$Low_SES == 0 & df$RELATION =="HPA-PNS reactivity"), ]
#13
k <- df[which(df$Low_SES == 1 & df$RELATION =="HPA-PNS reactivity"), ]
#3

k <- df[which(df$Low_SES == 0 & df$RELATION =="SNS-PNS baseline"), ]
#6
k <- df[which(df$Low_SES == 1 & df$RELATION =="SNS-PNS baseline"), ]
#2
k <- df[which(df$Low_SES == 0 & df$RELATION =="SNS-PNS reactivity"), ]
#7
k <- df[which(df$Low_SES == 1 & df$RELATION =="SNS-PNS reactivity"), ]
#2




# Adversity type
df$ADVERS_DI <- as.factor(df$ADVERS_DI)
moderator_adversity <- rma.mv(ES, variance, 
              mods = ~ RELATION:I(ADVERS_DI) - 1,
              random = ~ RELATION | ID, 
              slab = REF,
              method = "ML",
              #struct = "UN", #did not converge
              data =df)
print(moderator_adversity, digits = 3)
table(df$ADVERS_DI)


#Get ks
k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="HPA-SNS baseline"), ]
#20
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="HPA-SNS baseline"), ]
#8
k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="HPA-SNS reactivity"), ]
#30
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="HPA-SNS reactivity"), ]
#11

k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="HPA-PNS baseline"), ]
#10
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="HPA-PNS baseline"), ]
#5
k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="HPA-PNS reactivity"), ]
#14
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="HPA-PNS reactivity"), ]
#5

k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="SNS-PNS baseline"), ]
#7
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="SNS-PNS baseline"), ]
#4
k <- df[which(df$ADVERS_DI == 0 & df$RELATION =="SNS-PNS reactivity"), ]
#9
k <- df[which(df$ADVERS_DI == 1 & df$RELATION =="SNS-PNS reactivity"), ]
#4



```

### Test for biases 
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

#Sought guidance on stat exchange for testing biases for multivariate models:
#https://stats.stackexchange.com/questions/155693/metafor-package-bias-and-sensitivity-diagnostics
#The suggestions here are different than pre-reg, so will note that in paper

#Bias test #1: Egger's test (Egger et al., 1997)
test_egger <- rma.mv(ES,variance, 
                     mod = ~ RELATION:I(variance),
                     random = ~ RELATION | ID,  
                    #struct = "UN", #would not converge with this setting
                     slab = REF,
                     method = "ML",
                     data =df)
print(test_egger, digits = 3)


# Bias test #2: Cook's distance 
# cooks <- cooks.distance(main_model)
# plot(cooks, type="o", pch=19)
# png(filename = "CooksDistancePlot.png", 
#     width = 800, height = 640, 
#     pointsize = 12, res = 120)
# plot(cooks, type="o", pch=19)
# dev.off() #potentially one or two having a disproportionate influence on the overall summary estimate
# 
# summary(cooks)
# #    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
# # 0.00002 0.00381 0.03728 0.13454 0.13685 1.02214      77 
# 
# # View outliers with Cooks > 3 * mean
# outliers_cooks <- cooks %>% 
#   cbind(df$REF) %>%                   # bind study names for reference
#   subset(cooks > 3*0.13454) %>% # subset outliers
#   View() 
# # 4 outliers
# 
# #Select all cases except for outliers (figure out better way of doing this later bc the tidyverse way I tried kept failing and I dont have time)
# #Busso 2:7
# #Busso 3:8
# #Ellis 2: 32
# #Obradovic 1:84
# df_outliers_dropped <- df[c(1:6, 9:31, 33:83,85:127 ),]
# 
# #Run model without outliers
# main_model_outlier <- rma.mv(ES, variance, mods = ~ RELATION - 1,
#               random = ~ RELATION | ID, 
#               struct = "UN",
#               slab = REF,
#               method = "ML",
#               data = df_outliers_dropped)
# print(main_model_outlier, digits = 2)
#same effects so going with full model

```

## Descriptive plots:age
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

########age

dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS baseline')
AGE_HPASNS_base <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("HPA-SNS resting baseline") +
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_HPASNS_base.png", width = 4, height = 4)

dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS reactivity')
AGE_HPASNS_react <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("HPA-SNS reactivity")+
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_HPASNS_react.png", width = 4, height = 4)

dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS baseline')
AGE_HPAPNS_base <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("HPA-PNS resting baseline")+
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_HPAPNS_base.png", width = 4, height = 4)

dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS reactivity')
AGE_HPAPNS_react <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("HPA-PNS reactivity") +
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_HPAPNS_react.png", width = 4, height = 4)

dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS baseline')
AGE_SNSPNS_base <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("SNS-PNS resting baseline") +
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_SNSPNS_base.png", width = 4, height = 4)

dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS reactivity')
AGE_SNSPNS_react <- ggplot(dfplot, aes(x=AGE_MEAN_YRS, y=ES))+
  geom_point() +
  theme_classic () +
  stat_smooth(method=loess) +
  ylab("Effect size") +
  xlab("Mean sample age (years)") +
  ggtitle ("SNS-PNS reactivity")+
  scale_y_continuous(limits=c(-0.6, 0.6))
ggsave("AGE_SNSPNS_react.png", width = 4, height = 4)

```


## Descriptive plots: SES
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

########

dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS baseline') %>%
  filter(!is.na(Low_SES))
SES_HPASNS_base <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("") +
  ggtitle("HPA-SNS resting baseline")
ggsave("SES_HPASNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS reactivity') %>%
  filter(!is.na(Low_SES))
SES_HPASNS_react <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("") +
  ggtitle("HPA-SNS reactivity")
ggsave("SES_HPASNS_react.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS baseline') %>%
  filter(!is.na(Low_SES))
SES_HPAPNS_base <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("") +
  ggtitle("HPA-PNS resting baseline")
ggsave("SES_HPAPNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS reactivity') %>%
  filter(!is.na(Low_SES))
SES_HPAPNS_react <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  theme_classic() +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  ylab("Effect size") +
  xlab("") +
  ggtitle("HPA-PNS reactivity")
ggsave("SES_HPAPNS_react.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS baseline') %>%
  filter(!is.na(Low_SES))
SES_SNSPNS_base <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("") +
  ggtitle("SNS-PNS resting baseline")
ggsave("SES_SNSPNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS reactivity') %>%
  filter(!is.na(Low_SES))
SES_SNSPNS_react <- ggplot(dfplot, aes(x=as.factor(Low_SES), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Higher SES", "1" = "Lower SES")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("") +
  ggtitle("SNS-PNS reactivity")
ggsave("SES_SNSPNS_react.png", width = 4, height = 4)



```


## Descriptive plots: adversity
```{r, warning=FALSE, echo=TRUE, include=TRUE, message=FALSE}

########

dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS baseline') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_HPASNS_base <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("HPA-SNS resting baseline")
ggsave("ADVERS_HPASNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-SNS reactivity') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_HPASNS_react <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("HPA-SNS reactivity")
ggsave("ADVERS_HPASNS_react.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS baseline') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_HPAPNS_base <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("HPA-PNS resting baseline")
ggsave("ADVERS_HPAPNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'HPA-PNS reactivity') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_HPAPNS_react <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("HPA-PNS reactivity")
ggsave("ADVERS_HPAPNS_react.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS baseline') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_SNSPNS_base <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("SNS-PNS resting baseline")
ggsave("ADVERS_SNSPNS_base.png", width = 4, height = 4)


dfplot <- df %>% 
  filter(RELATION == 'SNS-PNS reactivity') %>%
  filter(!is.na(ADVERS_DI))
ADVERS_SNSPNS_react <- ggplot(dfplot, aes(x=as.factor(ADVERS_DI), y=ES)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, size = 1, color = "black") +
  scale_x_discrete(labels = c("0" = "Not present", "1" = "Present")) +
  scale_y_continuous(limits=c(-0.6, 0.6)) +
  theme_classic() +
  ylab("Effect size") +
  xlab("Sample adversity exposure") +
  ggtitle("SNS-PNS reactivity")
ggsave("ADVERS_SNSPNS_react.png", width = 4, height = 4)



```


